---
title: "homework 1"
author: "Weize Sun"
date: "9/25/2021"
output: html_document
---
```{r}
library(tidyverse)
```

## Problem 1
```{r}
hw1_df = 
  tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    operator = c("Thorns", "Surtr", "SilverAsh", "Ash", "Blaze", "Ifrit", "Mountain", "Archetto", "Dusk", "Broca"),
    job = factor(c("Guard", "Guard", "Guard", "Sniper", "Guard", "Caster", "Guard", "Sniper", "Caster", "Guard"))
  )

hw1_df

mean(pull(hw1_df, sample))
mean(pull(hw1_df, gr_than_0))
mean(pull(hw1_df, operator))
mean(pull(hw1_df, job))
```
When I tried to take the mean of each variable in my dataframe, I found only sample mean looks normal; logical vector's mean is 0.5, so I guess they took "true" and "false" as 0 and 1; both character vector (operator) and factor vector (job) couldn't give the means.

```{r eval=FALSE}
as.numeric(pull(hw1_df, gr_than_0))
as.numeric(pull(hw1_df, operator))
as.numeric(pull(hw1_df, job))
```
After I used the *as.numeric* and *pull* function, I found logical vectors have been changed to 0 and 1 (which confirmed my guess), because they only have "true" and "false" these two variables; character vectors have been changed to all "NA"s, because they are all different characters so that couldn't be changed to numbers; factor vectors have been changed to 1, 2, and 3, because there are total three categories so that 1, 2, and 3 could represent those categories.

## Problem 2
```{r}
data("penguins", package = "palmerpenguins")
names(penguins)
head(penguins)
skimr::skim(penguins)
nrow(penguins)
ncol(penguins)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("penguin_scatter_plot.pdf", height = 4, width = 6)

```

